%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

% Removes full stops from the end of cventrys
\usepackage{xpatch}
\xpatchcmd{\cventry}{.\strut}{\strut}{}{}

\usepackage{multicol}

% Page numbering. Remove this section for single page versions.
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\rfoot{\thepage\ of \pageref{LastPage}}
% End page numbering section

%Link colouring - see http://tex.stackexchange.com/questions/55950/how-to-change-the-color-of-the-hyperlink-to-mail-address-in-moderncv-class
\AtBeginDocument{
    \hypersetup{colorlinks,urlcolor=color2,linkcolor=color0}
}


%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Sam} % Your first name
\familyname{Frances} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
\address{Cambridge, UK}{}
%\mobile{(+33) 7 86 33 40 99}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{sam@samfrances.uk}
\homepage{samfrances.co.uk}
\social[homepage]{samfrances}
\social[github]{samfrances}
\social[linkedin]{samfrances}
%\extrainfo{}
%\photo[70pt][0.4pt]{picture} % The first bracket is the picture height, the second is %the thickness of the frame around the picture (0pt for no frame)

\quote{Experienced software engineer with with solid abilities in frontend and backend web development. I enjoy pushing myself to master new languages, frameworks, design patterns and programming paradigms.}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%   TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Technical Skills}


\begin{multicols}{2}

    % Line between columns:
    %\setlength{\columnsep}{1.5cm}
    %\setlength{\columnseprule}{0.2pt}

    \subsection{Languages}
    \cvitem{$\star\star\star$}{Python, TypeScript, Javascript,}
    \cvitem{}{TypeScript, HTML5, CSS3}
    \cvitem{$\star\star$}{SQL, C++}
    \cvitem{$\star$}{Go, Haskell, C, Erlang, Elixir}

    \subsection{Frameworks and libraries}

    \cvitem{$\star\star\star$}{Django, Django REST Framework,}
    \cvitem{}{Tornado, Redux}
    \cvitem{$\star\star$}{Qt, React, Jest, JQuery, Flask,}
    \cvitem{}{Celery}
    \cvitem{$\star$}{Aiohttp, Ansible, Jasmine,}
    \cvitem{}{Knockout, Google App Engine, Google}
    \cvitem{}{Cloud Endpoints}


    \columnbreak

    \subsection{Databases, caches, brokers etc.}

    \cvitem{$\star\star\star$}{Redis}
    \cvitem{$\star\star$}{SQLite}
    \cvitem{$\star$}{RabbitMQ, MongoDB}

    \subsection{Other}

    \cvitem{OS}{Ubuntu Linux}
    \cvitem{VCS}{Git/Github}
    \cvitem{Editors}{VSCode, Sublime, Vim}

\end{multicols}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}

\cventry{2021--current}{Senior Software Engineer}{Cydar Medical}{}{}{}
\cventry{2017--2020}{Front End Software Developer}{Cydar Medical}{}{}{
    \begin{itemize}
        \item{Member of development team for a growing medical SaaS company, providing cloud-based fusion imaging for surgical guidance.}
        \item{Created front-end of a project to allow clinicians make adjustments to aorta overlays during endovascular procedures. Implemented using Redux, Typescript, Jest and Python.}
        \item{Assisted with the design of an overhaul of Cydar's internal content-addressable storage service. Prototyped a "shared streams" mechanism allow more efficient downloads when multiple clients access the same files concurrently, using Python, Asyncio, Aiohttp and Boto.}
        \item{Worked on front-end and API endpoints for "Dynamic Morphology Correction" feature, using Typescript, Three.js, Python, Tornado and JSON-Schema.}
        \item{Led development of a cloud-based solution for presenting native 3D accelerated software in the browser.}
        \item{Architected and managed the rewrite of a microservice to orchestrate scaling of large pools of EC2 GPU workers, including a web-based control GUI, an improved incremental scale-down system, and greater reliability.}
    \end{itemize}
}
\cventry{2016--2017}{Junior Front End Developer}{Cydar Medical}{}{}{}
\cventry{2010--2016}{Public Affairs Executive}{The London Internet Exchange Ltd (LINX)}{}{}{}


%----------------------------------------------------------------------------------------
%   PROJECT EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Side Projects}

\cventry{ February 2019 }
    { Rejection App}{}{}
    {\href{ https://github.com/samfrances/rejection }{ github.com/samfrances/rejection }}
    {        \begin{itemize}
            \item{Frontend application built in TypeScript and React, and using the useState and useReducer hooks.}
        \end{itemize}
}
\cventry{ February 2019 }
    { C++ Two-Player Snake Clone}{}{}
    {\href{ https://github.com/samfrances/CppND-Capstone-Snake-Game }{ github.com/samfrances/CppND-Capstone-Snake-Game }}
    {        \begin{itemize}
            \item{An SDL-based two-player snake clone, developed using modern C++ techniques.}
        \end{itemize}
}
\cventry{ November 2019 }
    { C++ System Monitor App}{}{}
    {\href{ https://github.com/samfrances/CppND-System-Monitor-Project-Updated }{ github.com/samfrances/CppND-System-Monitor-Project-Updated }}
    {        \begin{itemize}
            \item{A simplified htop clone for monitoring a linux operating system.}
            \item{Developed in a test-driven manner using GoogleTest and GoogleMock.}
        \end{itemize}
}
\cventry{ April 2016 }
    { Kalah Game API}{}{}
    {\href{ http://www.github.com/samfrances/udacity-kalah }{ github.com/samfrances/udacity-kalah }}
    {        \begin{itemize}
            \item{Created an API for Kalah, a turn-based two-player "count and capture" board game.}
            \item{Written in Python using Google App Engine, Cloud Endpoints and Datastore.}
        \end{itemize}
}
\cventry{ February 2016 }
    { Catalog App}{}{}
    {\href{ http://github.com/samfrances/udacity-item-catalog }{ github.com/samfrances/udacity-item-catalog }}
    {        \begin{itemize}
            \item{Developed a content management system using the Flask framework in Python.}
            \item{Authentication is provided via OAuth and all data is stored within a PostgreSQL database.}
        \end{itemize}
}
\cventry{ November 2015 }
    { Swiss Tournament}{}{}
    {\href{ http://www.github.com/samfrances/udacity-swiss-system-tournament }{ github.com/samfrances/udacity-swiss-system-tournament }}
    {        \begin{itemize}
            \item{Designed and created a database for managing multiple Swiss-system tournaments simultaneously.}
            \item{Employed advanced SQL features such as views and triggers.}
        \end{itemize}
}
\cventry{ February 2015 }
    { Udacity Movies Website}{}{}
    {\href{ http://www.github.com/samfrances/udacity-movies-website }{ github.com/samfrances/udacity-movies-website }}
    {        \begin{itemize}
            \item{Single-page app to display information from the OMDb API, and combine with related trailers from Youtube.}
            \item{Combined both front- and back-end technologies, including Python, Bootstrap, JQuery, WSGI, HTML5.}
        \end{itemize}
}
\cventry{ February 2014 }
    { MVC todo list demo}{}{}
    {\href{ http://www.github.com/samfrances/todo-mvc-demo }{ github.com/samfrances/todo-mvc-demo }}
    {        \begin{itemize}
            \item{Simple Javascript todo list application, written as an exercise in creating an MVC Javascript application, without an MVC framework.}
        \end{itemize}
}


%----------------------------------------------------------------------------------------
%   CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Certifications and Professional Development}

\cventry{ 2019--current }
    {Software Development Micromasters}
    {Edx, UBCx}{}
    {}
    {        \begin{itemize}
            \item{ UBCx: How to Code - Simple Data, \href{ https://courses.edx.org/certificates/889346c63c2741d698ebc739811d0e5b }{ courses.edx.org/certificates/889346c63c2741d698ebc739811d0e5b } }
        \end{itemize}
}

\cventry{ 2016--current }
    {Computational Thinking using Python XSeries}
    {Edx, MITx}{}
    {}
    {        \begin{itemize}
            \item{ MITx: 6.00.1x Introduction to Computer Science and Programming Using Python, \href{ https://git.io/vK7kh }{ git.io/vK7kh } }
        \end{itemize}
}

\cventry{ 2019--2020 }
    {C++ Nanodegree}
    {Udacity}{}
    { \href{ https://confirm.udacity.com/7DDGS6J2 }{ confirm.udacity.com/7DDGS6J2 } }
    {}

\cventry{ 2018 }
    {JavaScript Foundations}
    {DevAnywhere.io}{}
    { \href{ https://www.credential.net/a796d867-1324-4698-bdb1-9f678cff402b }{ credential.net/a796d867-1324-4698-bdb1-9f678cff402b } }
    {}

\cventry{ 2016 }
    {Front-End Web Developer Nanodegree}
    {Udacity}{}
    { \href{ https://confirm.udacity.com/QJCGFPED }{ confirm.udacity.com/QJCGFPED } }
    {}

\cventry{ 2016 }
    {edX Computer Science}
    {HarvardX}{}
    {}
    {        \begin{itemize}
            \item{ CS50x Introduction to Computer Science, \href{ https://courses.edx.org/certificates/77c3400beb254e21a843faf77a20b518 }{ courses.edx.org/certificates/77c3400beb254e21a843faf77a20b518 } }
        \end{itemize}
}

\cventry{ 2015--2016 }
    {Full Stack Web Developer Nanodegree}
    {Udacity}{}
    { \href{ https://confirm.udacity.com/XD5UH24D }{ confirm.udacity.com/XD5UH24D } }
    {}

\cventry{ 2015 }
    {LINX Accredited Internet Technician 1}
    {Systems \& Network Training}{}
    {}
    {}

\cventry{ 2012--2013 }
    {Udacity computer science certificates}
    {Udacity}{}
    {}
    {        \begin{itemize}
            \item{ CS101 Introduction To Computer Science, \href{ https://git.io/vK7OQ }{ git.io/vK7OQ } }
            \item{ CS253 Web Development, \href{ https://git.io/vK7Op }{ git.io/vK7Op } }
            \item{ CS255 HTML5 Game Development, \href{ https://git.io/vK73T }{ git.io/vK73T } }
            \item{ CS262 Programming Languages, \href{ https://git.io/vK73Y }{ git.io/vK73Y } }
        \end{itemize}
}


%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{ 2009--2010 }
    { M. A. Linguistics}
    { University College London }{}{}{}

\cventry{ 2006--2009 }
    { B. A. Philosophy}
    { King's College London }{}{}{}



\end{document}
